What to simulate? Inferring the direction for mental rotation

### 2014-02-01 man/cogsci-2014/cogsci-2014.tex
Add note about human vs human corrs
Update results, add a few TODOs

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_time_corrs.pdf}
    \caption{\textbf{Angle vs. response time}}
    \label{fig:theta-time-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_accuracy_corrs.pdf}
    \caption{\textbf{Angle vs. accuracy}}
    \label{fig:theta-accuracy-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/human_model_corrs.pdf}
    \caption{\textbf{Human vs. model}}
    \label{fig:human-model-corrs}
  \end{subfigure}
  \vspace{10pt}
  \caption{\textbf{Correlations.} (a) Spearman correlations between
    the minimum angle of rotation and response time. (b) Spearman
    correlations between the minimum angle of rotation and
    accuracy. The \Oc{} and \Th{} models had 100\% accuracy;
    therefore, their correlations are undefined. (c) Pearson
    correlations between human and model, both for response time and
    accuracy. All error bars are 95\% confidence intervals.}
\end{figure*}

@@

For each model, we ran 50 samples for each stimulus that participants
viewed (with the exception of stimuli with rotations of $0^\prime$ or
$180^\prime$, in which case we ran double the number of samples). The
step size parameter ($\sigma_\epsilon$) was approximately fit to each
of the models, resulting in $\sigma_\epsilon=0.6$ for the \Bq{} model,
and $\sigma_\epsilon=0.1$ for all other models. We also ran the models
under two different priors, $p(h=0)=0.5$ (the ``equal'' prior) and
$p(h=0)=0.55$ (the ``unequal'' prior), though this only had an effect
for the \Bq{} model. \TODO{actually, did it affect HC?  check this}

@@

The average response time across all stimuli was \ExpTime{} seconds.
As illustrated in Fig.~\ref{fig:theta-time-corrs}, the minimum angle
of rotation was significantly monotonically correlated with average
per-stimulus response times, both for ``flipped'' and ``same''
pairs. While this replicates the general result of previous
experiments \cite<e.g.,>{Shepard1971,Cooper:1975wp}, our results are
not as perfectly linear. However, \citeA{Gardony:2013gn} found a
constant effect for ``flipped'' pairs; an average of their results and
the classic results would produce something similar to ours.

@@

As we would expect, the number of actions taken by the \Oc{} model was
perfectly correlated with the minimum angle of rotation
(Fig.~\ref{fig:theta-time-corrs}), both for ``same'' and ``flipped''
pairs. Unsurprisingly, then, \Oc{} model was the best fit to human
response times, with a correlation of \OcTimeCorr{}
(Fig.~\ref{fig:human-model-corrs}).  However, the \Oc{} model was
100\% accurate, and therefore the correlation between minimum angle
and accuracy was undefined (Fig.~\ref{fig:theta-accuracy-corrs}).

@@

@@

The \Hc{} was the only model for which there was no effect of rotation
on response time (Fig.~\ref{fig:theta-time-corrs}). Although there was
a significant effect of rotation on accuracy
(Fig.~\ref{fig:theta-accuracy-corrs}), the \Hc{} model was barely
above chance (\HcAccuracy{}) and there were \HcNumChance{} individual
stimuli for which it was not above chance. The \Hc{} model was not a
particularly good predictor of human response times (\HcTimeCorr{}),
though it was a moderate predictor of accuracy (\HcAccuracyCorr{}), as
shown in Fig.~\ref{fig:human-model-corrs}.

@@

The \Bq{} model was quite accurate overall, both with the equal prior
(\BqAccuracy{}) and unequal prior (\BqpAccuracy{}). With the equal
prior, there was \BqNumChance{} stimulus for which it was not above
chance; with the unequal prior, there were \BqpNumChance{}. There was
a significant effect of rotation on the \Bq{} model's accuracy
(Fig.~\ref{fig:theta-accuracy-corrs}), and itt explained about the
same amount of variance in people's accuracy as the \Hc{} model: for
the equal prior, \BqAccuracyCorr{}; for the unequal prior,
\BqpAccuracyCorr{}.

>>>>

\TODO{need to compute better human vs human correlations}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_time_corrs.pdf}
    \caption{\textbf{Angle vs. response time}}
    \label{fig:theta-time-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/theta_accuracy_corrs.pdf}
    \caption{\textbf{Angle vs. accuracy}}
    \label{fig:theta-accuracy-corrs}
  \end{subfigure}%
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[width=\textwidth]{../../figures/D/human_model_corrs.pdf}
    \caption{\textbf{Human vs. model}}
    \label{fig:human-model-corrs}
  \end{subfigure}
  \vspace{10pt}
  \caption{\textbf{Correlations.} (a) Spearman correlations between
    the minimum angle of rotation and response time. (b) Spearman
    correlations between the minimum angle of rotation and
    accuracy. The \Oc{} and \Th{} models had 100\% accuracy;
    therefore, their correlations are undefined. (c) Pearson
    correlations between human and model, both for response time and
    accuracy. The first set of bars is human vs. human, to give an
    upper bound. All error bars are 95\% confidence intervals.}
\end{figure*}

@@

For each model, we ran 50 samples for each stimulus that participants
viewed (with the exception of stimuli with rotations of $0^\prime$ or
$180^\prime$, in which case we ran double the number of samples). The
step size parameter ($\sigma_\epsilon$) was fit to human data for each
of the models, resulting in $\sigma_\epsilon=0.6$ for the \Th{} and
\Bq{} models and $\sigma_\epsilon=0.1$ for the \Oc{} and \Hc{}
models. We also ran the models under two different priors,
$p(h=0)=0.5$ (the ``equal'' prior) and $p(h=0)=0.55$ (the ``unequal''
prior). This had an effect on accuracy for the \Hc{} model, and an
effect on both accuracy and response time for the \Bq{} model. Below,
we report results for the \Hc{} model with an unequal prior, and the
\Bq{} model with both priors.

@@

The average response time across all stimuli was \ExpTime{}
milliseconds.  As illustrated in Fig.~\ref{fig:theta-time-corrs}, the
minimum angle of rotation was significantly monotonically correlated
with average per-stimulus response times, both for ``flipped'' and
``same'' pairs. While this replicates the general result of previous
experiments \cite<e.g.,>{Shepard1971,Cooper:1975wp}, our results are
not as perfectly linear. However, \citeA{Gardony:2013gn} found a
constant effect for ``flipped'' pairs; an average of their results and
the classic results would produce something similar to ours.

@@

As we would expect, the number of actions taken by the \Oc{} model was
perfectly correlated with the minimum angle of rotation
(Fig.~\ref{fig:theta-time-corrs}), both for ``same'' and ``flipped''
pairs. Unsurprisingly, the \Oc{} model was the best fit to human
response times, with a correlation of \OcTimeCorr{}
(Fig.~\ref{fig:human-model-corrs}).  However, the \Oc{} model was
100\% accurate, and therefore the correlation between minimum angle
and accuracy was undefined (Fig.~\ref{fig:theta-accuracy-corrs}).

@@

\TODO{say something about the large step size -- actually produces
  non-intuitive results, even though they are a better fit. with small
  step size (where it doesn't over-rotate) it does even worse!}

@@

The \Hc{} was the only model for which there was no effect of rotation
on response time (Fig.~\ref{fig:theta-time-corrs}). Although there was
a significant effect of rotation on accuracy
(Fig.~\ref{fig:theta-accuracy-corrs}), the \Hc{} model was barely
above chance (\HcAccuracy{}) and there were \HcNumChance{} individual
stimuli for which it was not above chance. The \Hc{} model was not a
particularly good predictor of human behavior, neither for response
times (\HcTimeCorr{}) nor accuracy (\HcAccuracyCorr{}), as shown in
Fig.~\ref{fig:human-model-corrs}.

@@

The \Bq{} model was quite accurate overall, both with the equal prior
(\BqAccuracy{}) and unequal prior (\BqpAccuracy{}). With the equal
prior, there was \BqNumChance{} stimulus for which it was not above
chance; with the unequal prior, there were \BqpNumChance{}. There was
a significant effect of rotation on the \Bq{} model's accuracy
(Fig.~\ref{fig:theta-accuracy-corrs}), and it explained about the same
amount of variance in people's accuracy as the \Hc{} model: for the
equal prior, \BqAccuracyCorr{}; for the unequal prior,
\BqpAccuracyCorr{}.
